%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Cloud-Native Software Engineer} % Job title
{NetApp} % Organization
{Seattle, WA} % Location
{Jan. 2019 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and developed the cluster provision system that is the backbone of "NKS" (NetApp Kubernetes Service), a multi-cloud, production-grade, managed Kubernetes offering that leverages several upstream Kubernetes SIG (special interest group) projects.}
\item {Built Ansible playbooks and provided documentation for the support team to provide services to NKS customers more efficiently.}
\item {Collaborated with front-end team to design and develop an API for the build system using gRPC.}
\item {Contributed to Cluster API Kubernetes SIG via Github pull requests and issues, Zoom office hours and Slack discussions.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Site Reliability Engineer} % Job title
{Drud} % Organization
{Seattle, WA} % Location
{Jul. 2018 - Dec. 2018} % Date(s)  
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Operated and iterated on "DDEV Live", a Kubernetes-based web-hosting platform and deployment pipeline for hundreds of CMS websites.}
\item {Established and executed plan to deliver 99.99\% uptime guarantee by implementing self-healing HA platform with resource-based autoscaling.}
\item {Instrumented, configured, and tuned observability and monitoring stack using Prometheus metrics and alert dashboard, Fluentd, and LogDNA, with VictorOps and Slack integrations, which provided the foundation for new on-call rotations.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer / DevOps Engineer} % Job title
{MedBridge} % Organization
{Seattle, WA} % Location
{Jan. 2015 - Jul. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Led effort to move deployment platform from Puppet to Kubernetes, which included translating Puppet manifests into Dockerfiles and Kubernetes specs and adopting technologies such as KOPS, Helm, Minikube, ELK stack, Kubectl, and Calico network policies.}
\item {Reviewed and updated MedBridge services to ensure they met cloud-native best practices.}
\item {Designed active-active failover system to ensure MedBridge services met and exceeded SLA requirements.}
\item {Implemented cluster monitoring, logging, and alerting system using several open source projects.} 
% \item {Onboard and remained an ongoing resource for the development team for Kubernetes workflow via documentation, demos, and 1-on-1 sessions in order to ensure developer and application success.}
\item {Containerized / Dockerized PHP, Golang, and Node applications and wrote manifest files to bring them to life in a Kubernetes cluster.}
\end{cvitems}
}

%------------------------------------------------

% \cventry
% {Software Engineer} % Job title
% {McGraw-Hill} % Organization
% {Seattle, WA} % Location
% {Jun. 2017 - Sep. 2017} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Built CI/CD pipeline for PHP web app using CircleCI, Docker, Terraform, Vault, and AWS ECS (EC2 Container Service).}
% \item {Redesigned PHP/Nginx Docker images with performance and security in mind in order to make containerized app production ready.}
% \item {Contributed various features and bug fixes to PHP web app.}
% \end{cvitems}
% }

\cventry
{Software Engineer} % Job title
{HCSS} % Organization
{Sugar Land, TX} % Location
{Mar. 2014 - Dec. 2014} % Date(s)
{
\begin{cvitems}
\item {Built tools in C\#/.NET to manage and sync data between Azure and on-prem servers.}
\item {Wrote custom reports in SQL based on customer needs.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Web Programmer} % Job title
{R.R. Donnelley} % Organization
{Houston, TX} % Location
{Dec. 2012 - Mar. 2014} % Date(s)
{
\begin{cvitems}
\item {Developed UIs in HTML, CSS, and JavaScript for web-to-print, variable-data print products.}
\end{cvitems}
}

\end{cventries}
